Distinguishing Between Spin-Aligned and Isotropic Binary Black Hole Populations Using Gravitational Wave Observations

### 2017-03-27 paper/AlignedIsotropicGW.tex
Removed some un-printable characters and added arXiver comment line.

@@

The classical isolated binary evolution channel \citep{TutukovYungelson:1973,TutukovYungelson:1993,Lipunov:1997,Dominik:2015} through the
common-envelope (CE) phase \citep{Ivanova:2013} 
yields the following typical formation channel for
binary black holes: possible mass transfer from the primary to the
secondary; the collapse of the primary into a BH; the formation and
ejection of a CE as a consequence of dynamically unstable mass
transfer from the secondary to the primary; possible further mass
transfer from remaining secondary core to primary; collapse of the
secondary into a BH; a merger induced by GW emission
\citep[e.g.,][]{2016Natur.534..512B,Stevenson:2017}.  Interaction
before the collapse of the primary could realign the binary, but the
primary'۪s spin in the wide (separation $\gtrsim 10$ AU) binary can
easily be misaligned by even moderate \citep{Mandel:2015kicks}
natal kicks.  Realignment of the primary through subsequent mass
accretion is unlikely given the small amount of accreted mass, except
perhaps during hyper-critical accretion during CE \citep{2005ApJ...632.1035O}, though even this accretion is likely to be small according to recent results \citep{MacLeodRamirezRuiz:2015}; realignment through dissipation in the possibly warped
accretion disk \citep{1975ApJ...195L..65B} is possible, but calculations
suggest it is unlikely for stellar-mass binaries \citep{KLOP}.

The secondary should tidally align with the orbit before the onset of
mass transfer
\citep[e.g.,][]{2000ApJ...541..319K,2013PhRvD..87j4028G}; however,
most of its angular momentum would be lost to the envelope, which will
be ejected during the CE phase.  The remnant core may or may not be
efficiently re-aligned, depending on the separation between the
secondary's core and the BH immediately after the CE is ejected
\citep{2016MNRAS.462..844K}.  The secondary'۪s natal kick will be small
relative to the orbital velocity of the close post-CE binary, so any
further kick-induced misalignment will be moderate
\citep{2016ApJ...832L...2R}.

>>>>

% arXiver will snag the right plots so they show up on Twitter :)
%@arxiver{chi-eff-distributions.pdf,Wills_evidence_ratio_figure_with_mixture_models.png,chi-eff-mock-posteriors.pdf,six-way-O2-model-selection.pdf}

@@

The classical isolated binary evolution channel \citep{TutukovYungelson:1973,TutukovYungelson:1993,Lipunov:1997,Dominik:2015} through the
common-envelope (CE) phase \citep{Ivanova:2013} 
yields the following typical formation channel for
binary black holes: possible mass transfer from the primary to the
secondary; the collapse of the primary into a BH; the formation and
ejection of a CE as a consequence of dynamically unstable mass
transfer from the secondary to the primary; possible further mass
transfer from remaining secondary core to primary; collapse of the
secondary into a BH; a merger induced by GW emission
\citep[e.g.,][]{2016Natur.534..512B,Stevenson:2017}.  Interaction
before the collapse of the primary could realign the binary, but the
primary's spin in the wide (separation $\gtrsim 10$ AU) binary can
easily be misaligned by even moderate \citep{Mandel:2015kicks}
natal kicks.  Realignment of the primary through subsequent mass
accretion is unlikely given the small amount of accreted mass, except
perhaps during hyper-critical accretion during CE \citep{2005ApJ...632.1035O}, though even this accretion is likely to be small according to recent results \citep{MacLeodRamirezRuiz:2015}; realignment through dissipation in the possibly warped
accretion disk \citep{1975ApJ...195L..65B} is possible, but calculations
suggest it is unlikely for stellar-mass binaries \citep{KLOP}.

The secondary should tidally align with the orbit before the onset of
mass transfer
\citep[e.g.,][]{2000ApJ...541..319K,2013PhRvD..87j4028G}; however,
most of its angular momentum would be lost to the envelope, which will
be ejected during the CE phase.  The remnant core may or may not be
efficiently re-aligned, depending on the separation between the
secondary's core and the BH immediately after the CE is ejected
\citep{2016MNRAS.462..844K}.  The secondary's natal kick will be small
relative to the orbital velocity of the close post-CE binary, so any
further kick-induced misalignment will be moderate
\citep{2016ApJ...832L...2R}.
